SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-19 maintex.tex
Fixed typos/Revised Future work

\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\reff}{$R_{\rm eff}$}
\newcommand{\ewha}{EW(H$\alpha$)}
\newcommand{\logm}{log({\it M}/M$_{\odot}$)}
%\newcommand{\arcsec}{\prime\prime}
\newcommand{\simard}{Simard+11}

@@

\author{
Joshua L. Steffen\altaffilmark{1}, 
Hai Fu\altaffilmark{1}, and 
MaNGA Team 
}
\altaffiltext{1}{Department of Physics \& Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. We also find that the sSFR offsets in the outskirts of the paired galaxies is dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences no to a positive sSFR enhancement while the less massive companion experiences a sSFR suppression in their outskirts.
\end{abstract}

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_i+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_i+18)
\end{equation}

@@

We supplement the inside-IFU sample with a set of pairs identified outside of the field of view of the MaNGA IFU. We select these outside-IFU pairs from the NSA catalog. We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of $r_p$ $<$ 50 kpc using the MaNGA target's redshift. We further use a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.

@@

To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of isolated galaxies in the MaNGA survey. We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_p$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a control sample of 1888 star forming control galaxies.

@@

%%% Reddening
We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.

We measure the SFR from the extinction corrected H$\alpha$ luminosity, L$_{{\rm H}\alpha}$.  We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.

\begin{equation}\label{eq:sfr}
\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{{\rm L}_{H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
\end{equation}

@@

\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M^*}
\end{equation}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into four different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. }
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}. We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the median profile of the control galaxies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}
%\centering
%\includegraphics[width=\linewidth]{fig/ssfr_massdm.pdf}
%\caption[]{Same as the left hand panel of Figure \ref{fig:ssfr_mass} except primary companions are shown on the \textbf{Left} and secondary companions are shown on the \textbf{Right}. The \logm\ $=$ 11.0$-$11.5 mass bin is left out of left hand panel since it only contains two galaxies. }
%\label{fig:ssfr_massdm}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We will define the more massive galaxies of a pair, $\Delta$log(M) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log(M) $<$ 0.0, the secondary companion.

@@

In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log(M)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log(M)$|$ $>$ 0.5. Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers. Secondary companions also feature slightly higher levels of enhancement in their centers than primary companions at the same mass ratios by $\sim$0.1 dex.

@@

In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.3 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0. We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.

@@

The dependency of the SFR enhancement on the mass ratio was studied in \citet{Ellison:2008}. They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios. We find that pairs with mass ratios of $\Delta$log(M) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log(M) $=$ 1.0 (10:1). \citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs. We not only confirm that secondary companions of minor pairs feature SFR enhancement, but also that the enhancement is higher than the primary component of pairs at the same mass ratios.

@@

\subsection{Enhanced Pairs or Quenched Controls}

In Figure \ref{fig:ssfr_prof}, we showed the stacked sSFR profiles of control galaxies and paired galaxies. The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}). The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching. This indicates that the central offsets viewed in the difference profiles is largely driven by the centrally quenched controls. Because of this it may be more proper to describe isolated galaxies as being centrally quenched or that the profiles of paired galaxies are flattened in their centers with respect to their controls.

The flattening of the paired galaxies' profiles seems to indicate that the merger event can ``un-quench" the centers of the galaxies. The mode of inside-out quenching that seems most consistent with our results is the gas depletion model where the galaxy runs out of cold gas in their centers. In the merger event, new gases are brought into the centers of the galaxies by the merger induced gas inflows which are then able to facilitate new star formation.

After the merger induced starburst, it is unclear whether the galaxy will return to the same level of central quenching or if the resulting galaxy is more quenched. From Figure \ref{fig:ssfr_prof}, we see that more massive galaxies are more quenched than less massive galaxies. Since the resulting galaxy after the merger process will be more massive than it was before and since the most massive galaxies have likely gone through multiple past merging events \citep{Rodriguez-Gomez:2016, Pillepich:2018}, it is reasonable to believe that the long term result of the merger event is a more quenched galaxy. In this situation, the merger event temporarily alleviates the galaxy from its quenched state; however, when starburst ends the galaxy is more quenched than it was before.

@@

\begin{enumerate}
\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
\item The outskirts of the paired galaxies, \reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies.
\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies. Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey. Paired galaxies with large mass ratios, $|\Delta$log(M)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex. 
\item The secondary companions of a galaxy pair, the less massive galaxy, show higher sSFR enhancements, by $\sim$0.1 dex in comparison to primary companions at the same mass ratio. Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.3 dex. Secondary companions feature a sSFR suppression in their outskirts of 0.0$-$0.3 dex.
\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$15 kpc have their sSFR enhanced by 0.3$-$0.4.

\end{enumerate}

>>>>

\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\reff}{$R_{\rm eff}$}
\newcommand{\ewha}{EW(H$\alpha$)}
\newcommand{\logm}{log($M/M_{\odot}$)}
%\newcommand{\arcsec}{\prime\prime}
\newcommand{\simard}{Simard+11}

@@

\author{
Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1}, J.~M.~Comerford\altaffilmark{2}, Shuai~Feng\altaffilmark{3}, Cheng~Li\altaffilmark{4}, Y.~Sophia~Dai\altaffilmark{5}, and Rui~Xue\altaffilmark{1}
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
\altaffiltext{2}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
\altaffiltext{3}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
\altaffiltext{4}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}
\altaffiltext{5}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 175 star-forming galaxies in close pairs with those of mass-matched isolated galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. We also find that the sSFR offsets in the outskirts of the paired galaxies is dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.
\end{abstract}

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18)
\end{equation}

@@

We supplement the inside-IFU sample with a set of pairs identified outside of the field of view of the MaNGA IFU. We select these outside-IFU pairs from the NSA catalog. We search for these external pairs by selecting objects with a projected separation from the MaNGA targets of $r_{\rm p}$ $<$ 50 kpc using the MaNGA target's redshift. We further use a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$ to remove projected galaxies from the selection.

@@

To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of isolated galaxies in the MaNGA survey. We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a control sample of 1888 star forming control galaxies.

@@

%%% Reddening
We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_{\rm V}$ $\equiv$ $A_{\rm V}/E(B-V)$ $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination.

We measure the SFR from the extinction corrected H$\alpha$ luminosity, $L_{{\rm H}\alpha}$.  We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination.

\begin{equation}\label{eq:sfr}
\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}
\end{equation}

@@

\begin{equation}
{\rm sSFR} = \frac{\rm SFR}{M_*}
\end{equation}

@@

The control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with higher stellar masses (which was previously seen in the MaNGA survey in \citet{Belfiore:2018}). The paired galaxies show flattened star formation profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5 which still show some central quenching.

@@

It is also relevant to note that the driving factor behind the central enhancement to the sSFR in the difference profiles is really the quenching in the centers of the controls. While the mechanism for the quenching in galaxies is in dispute, the merger process seems to be capable of rejuvenating star formation in the centers of these galaxies resulting in the flatter sSFR profiles seen in the paired galaxies. Further, since the sSFR enhancement in the difference profiles is largely driven by the quenched controls, it may be more appropriate to describe isolated galaxies as being centrally quenched in comparison to paired galaxies or that the profiles of paired galaxies are flattened in their centers with respect to their controls.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. In the \textbf{Right} panel the nuclear $\Delta$log(sSFR) are shown. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by mass ratio. The inside-IFU sample is left out of this analysis as their mass ratios are unreliable.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in Section \ref{sec:control}. We take the individual azimuthally averaged profiles of the selected control galaxies and take the median value of the profiles at each radius bin to produce the median profile of the control galaxies.

@@

@@

Where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of the companion galaxy. We will define the more massive galaxies of a pair, $\Delta$log($M$) $>$ 0.0, the primary companion and the less massive galaxy of a pair, $\Delta$log($M$) $<$ 0.0, the secondary companion.

@@

In the top left of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5. Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers. Secondary companions also feature slightly higher levels of enhancement in their centers than primary companions at the same mass ratios by $\sim$0.1 dex.

@@

In the top right of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio, $\Delta$log($M$) $=$ 0.0. These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0. We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.

@@

The dependency of the SFR enhancement on the mass ratio was studied in \citet{Ellison:2008}. They found that pairs with mass ratios of 2:1 have higher SFR enhancements of $\sim$0.1 dex over pairs with wider 10:1 mass ratios. We find that pairs with mass ratios of $\Delta$log($M$) $=$ 0.25 (1.8:1) are 0.2 dex over pairs with mass ratios of $\Delta$log($M$) $=$ 1.0 (10:1). \citet{Ellison:2008} also saw tentative evidence for SFR enhancement in the secondary companions of minor pairs. We not only confirm that secondary companions of minor pairs feature SFR enhancement, but also that the enhancement is higher than the primary component of pairs at the same mass ratios.

@@

@@

\begin{enumerate}
\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
\item The outskirts of the paired galaxies, \reff\ $=$ 1.0$-$2.5, show limited suppression in their disks of $\sim$0.1 dex.
\item The sSFR enhancement in paired galaxies is independent of their total stellar mass.
\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies. Galaxies with small mass ratios, $|\Delta$log($M$)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.35 dex, which is 0.1 dex higher than the average paired galaxies in the survey. Paired galaxies with large mass ratios, $|\Delta$log($M$)$|$ $=$ 1.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex. 
\item The secondary companions of a galaxy pair, the less massive galaxy, show higher sSFR enhancements, by $\sim$0.1 dex in comparison to primary companions at the same mass ratio. Further, primary companions have zero to positive sSFR offsets in their ouskirts, $\Delta$log(sSFR) $=$ 0.0$-$0.4 dex. Secondary companions feature a sSFR suppression in their outskirts of 0.1$-$0.4 dex.
\item The sSFR enhancement increases with closer projected separations where galaxies within 20 kpc have their sSFR enhanced by 0.3$-$0.4. 
\end{enumerate}

There is still much to be understood about these galaxy pairs. We see that there is a great diversity in the difference profiles of individual galaxies. In particular there are galaxy pairs which feature a strong suppression to the sSFR in their centers while others feature a central enhancement to the sSFR which is much greater than the median enhancement. The depth of our analysis here would benefit by studying other merger parameters like the interaction stage or the gas fraction.

As of August 24, 2020, MaNGA has finished observing its goal of 10,000 galaxies. The completion of the final sample will mean that we will have access to a larger sample of paired and control galaxies. We also plan to fit the light profiles of the inside-IFU companion galaxies which will allow us to roughly double the size of the inside-IFU sample. With this and the completion of MaNGA's observations, we may be able to expand our pair sample to include nearly 500 galaxy pairs.

With the larger sample size we will be better able to separate how the stellar mass, mass ratio, and projected separation effect the enhancement profile along with new parameters like the merger stage and gas fraction. Also, by constructing enhancement profiles for the inside-IFU companions to the MaNGA targets, we can better study how primary companions behave in comparison to their secondary companions.
